---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
```

```{r}
phones <- read_csv("../../../CodeClan_Homework_Struan/week_06/day_2/data/20190928-items.csv")
```

```{r}
phones <- phones %>% 
  clean_names()
```

```{r}
phones_selected <- phones %>% 
  select(brand, title, rating, total_reviews)
```

# Question 2.
Find the brand with the highest numbers of phones in the dataset.

```{r}
top_brand <- phones_selected %>% 
  group_by(brand) %>% 
  count(brand)
```

Samsung has the most number of brands out of all the phones. 

# Question 3.

For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution.

```{r}
samsung_stats <- phones %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    num = n(),
    mean = mean(rating),
    sd = sd(rating)
  )
```

```{r}
samsung <- phones_selected %>% 
  filter(brand == "Samsung") %>% 
  ggplot(aes(x = rating))+
  geom_histogram(aes(y = after_stat(density)), col = "white") +
  stat_function(
    fun = dnorm,
    args = list(
      mean = samsung_stats$mean,
      sd = samsung_stats$sd
    ),
    col = "steelblue"
  )
  

```

 Do you think the normal distribution provides a good model of these ratings?
 
The normal distribution provides a good structure of how the ratings have been allocated but it struggles to highlight the high density of ratings the Samsung phones were given. 

```{r}
phones_selected %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    mean_reviews = mean(rating),
    median_reviews = median(rating),
    mode_reviews = mode(rating)
  )
```

The mean reviews are 3.57, the median is 3.6 and the mode is unknown due to it being a string character rather than numeric. 
```{r}
phones_selected %>% 
  filter(brand == "Samsung") %>% 
  summarise(skewness = skewness(rating, type = 1))
```
The data is moderately skewed. 

```{r}
phones_selected %>% 
  filter(brand == "Samsung") %>% 
  summarise(
    Q1 = quantile(rating, 0.25),
    Q2 = quantile(rating, 0.5),
    Q3 = quantile(rating, 0.75),
    IQR = Q3 - Q1,
    range = diff(range(rating))
  )
```
```{r}
ggplot(samsung_stats, aes(x = rating))+
  geom_boxplot()
```


# Question 4.
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the mean() and sd() of your distribution in an earlier question. Use these values to calculate the proportions of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.

1 Standard Deviation 

```{r}
samsung_stats %>%
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```

