---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
backpack
```

# Question 2.

#What is the distribution of backpack weights that students are carrying? Choose an appropriate graph to show the distribution.

```{r}
ggplot(backpack)+
  geom_histogram(aes(x = backpack_weight), colour = "white", fill = "grey20")+
  labs(x = "Backpack Weight", title = "Backpack Weight Distribution")
```

#The majority of packpacks are around the 10-15lb weight category with only a few being much heavier. 

# Question 3.

#Are there differences in backpack weight between sex?

```{r}
ggplot(backpack) +
  geom_histogram(aes(x = backpack_weight, fill = sex), position = "dodge")
```
#Women have a slight preference for lighter backpacks but otherwise there is very little difference. 

# Question 4.

#What is the relationship between body weight and backpack weight?

```{r}
ggplot(backpack)+
  geom_point(aes(x = body_weight, y = backpack_weight))+
  geom_smooth(aes(x = body_weight, y = backpack_weight))
```

#There is very little correlation between body weight and backpack weight.

# Question 5.

#Is this relationship different between men and women? Choose an appropriate plot and interpret your findings. 

```{r}
ggplot(backpack)+
  geom_point(aes(x = body_weight, y = backpack_weight, colour = sex))
```
#Still no correlation when it comes to gender. 

# Question 6.

#What proportion of students report back pain?

```{r}
ggplot(backpack)+
  geom_bar(aes(x = back_problems))+
  coord_polar()
```

# Question 7.

#Is this proportion different between men and women?


# Question 8 

#Now you’ve investigated your data separately, create plots to describe the relationship between backpack weight, body weight, gender and reported backpain.

```{r}
ggplot(backpack)+
  geom_col(aes(x = backpack_weight, y = body_weight))+
  facet_wrap(~sex ~back_problems)
```
#I don't think this is right as the data seems to have no correlation
