---
title: "House Price Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(GGally)
library(ggfortify)
library(mosaic)
```

```{r}
housing_prices <- read_csv("data/housing_prices.csv")
```

```{r message=FALSE, warning=FALSE}
ggpairs(housing_prices)
```

```{r}
housing_prices %>% 
  ggplot(aes(x = total_rooms, y = total_bedrooms))+
  geom_point()
```

```{r}
housing_prices_drop <- housing_prices %>% 
  select(-total_bedrooms)
```

```{r message=FALSE, warning=FALSE}
ggpairs(housing_prices_drop)
```

```{r}
housing_prices_drop %>% 
  ggplot(aes(x = median_house_value, y = total_rooms))+
  geom_point()
```

```{r}
housing_prices_drop %>% 
  distinct(ocean_proximity)
```

There are 5 variables but it would create 4 dummy variables because one can be realised. 

```{r}
housing_prices_drop %>% 
  ggplot(aes(x = median_house_value, y = median_income))+
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
model <- lm(median_house_value ~ median_income, data = housing_prices_drop)

autoplot(model)
```

There is a massive cluster of point but they stay relatively close to the zero on residuals vs fitted, they mostly stay on the line in Normal Q-Q and there seems to be low heteroskedasticity/funnels. 

```{r}
summary(model)
```


```{r}
model2 <- lm(median_house_value ~ median_income + total_rooms, data = housing_prices_drop)
```

```{r}
autoplot(model2)
```

The second model seems pretty similar to the first. Slightly worse with less of a shotgun spread on residual vs fitted, more off the line  in normal Q-Q and there is some evidence of heteroskedacicity on scale-location. However it seems workable. 

```{r}
summary(model2)
```

```{r}
plotModel(model2)
```

