---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
library(janitor)
```

Question 1

```{r}
Card_Base <- read.csv("data/CardBase.csv")
```
```{r}
Customer_Base <- read.csv("data/CustomerBase.csv")
```

```{r}
Fraud_Base <- read_csv("data/FraudBase.csv")
```

Cleaned names for consistent format. So that everyone else is on the same page and it is easier to remember the format. 

```{r}
Transaction_Base <- read_csv("data/TransactionBase.csv") %>% 
  clean_names()
```

Question 2

```{r}
left_join(Card_Base, Customer_Base, "Cust_ID")
```

Question 3

```{r}
full_join(Transaction_Base, Fraud_Base, by = "Transaction_ID")
```
Question 4

```{r}
Card_Base
Transaction_Base
semi_join(Card_Base, Transaction_Base, by = c("Card_Number" = "Credit_Card_ID"))
```
# Tidyr


```{r}
hat_observations <- read.csv("data/hat_observations.csv")
```

Question 1

```{r}
hat_split <- hat_observations %>% 
  separate(observation, c("hat_colour", "hat_type"), sep = "\\,")
           
hat_split

```

Question 2

```{r}
hat_dates <- hat_split %>% 
  unite(date, c("day", "month", "year"), sep = "/")

hat_dates
```

```{r}
hat_dates %>% 
  count(hat_colour)
```

reduce the dataset to berets, trying to understand that I need to filter out hat types to just get berets. I need to put it in quotation marks so that the item can be highlighted as a variable. Beret is a string value, and strings have to be in quotes. 

Got to the mutate statement by using the help file and scrolling through "after." 

```{r}
hat_dates %>% 
  mutate(is_beret = hat_type == "beret", .after = hat_type) %>% 
  filter(is_beret)
```

I have learned to filter for hat type so that we can narrow the data down to just berets. I then grouped up the dates so that the dates counted the number of berets per day. I lastly summarised the data so that we were given a total sum for each day the berets were present. 

I used the summarise function to give one row per group.
The word total will create a new column called total. 
The new column total will contain the sum of the observation counts for each date. 

```{r}
hat_dates %>% 
filter(hat_type == "beret") %>% 
  group_by(date) %>% 
  summarise(total = sum(observation_count))
```

# Extension

Question 1 

```{r}
Card_Base %>% 
  inner_join(Customer_Base, by = "Cust_ID") %>% 
  inner_join(transaction_base, by = c("card_number" = "credit_card_id")) %>% 
  inner_join(fraud_base, by = "transaction_id")
```

Question 2

```{r}
exam_scores <- read.csv("data/exam_scores.csv")
```

```{r}
exam_scores_long <- exam_scores %>% 
  pivot_longer(exam_Q1:exam_Q10, names_to = "exam_question", values_to = "score") 

exam_scores_long %>% 
  separate(exam_question, sep = "Q", into = c("extra_column", "exam_question")) %>% 
  select(-extra_column)
```

