---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
library(CodeClanData)
```
```{r}
library(tidyverse)
here::here()
```
```{r}
books <- read_csv("")
```


```{r}
library(janitor)

```
#movie data

```{r}
movies <- read_csv("data/movies.csv")
```

```{r}
movies %>% 
  glimpse()
```
#dimensions of dataset

```{r}
dim(movies)
```

```{r}
view(movies)
```

#total number of missing values in dataset

```{r}
sum(is.na(movies))
```

#how many rows are lost if you drop the NAs

```{r}
nrow(movies) - nrow(drop_na(movies))
```

```{r}
movies_selected <- movies %>% 
  select(title, runtime, budget)

movies_selected
```


```{r}
movies_selected <- movies %>% 
  select("title", "runtime", "budget")
  
```


```{r}
movies_selected %>% 
glimpse()
```

```{r}
movies_selected %>% 
  mutate(runtime = na_if(runtime, "0"))
```
```{r}
?na_if
```

```{r}
movies %>% 
  mutate(budget_type = case_when
         budget %% < 12000000 ~ "Small budget",
         budget %% < 40000000 ~ "Medium budget",
         budget %% > 40000000 ~ "Big budget")
```

```{r}
movies_selected %>% 
  summarise(na_runtime = sum(is.na(runtime)),
            na_title = sum(is.na(title)),
            na_budget = sum(is.na(budget)))
```

```{r}
movies_runtime <- movies_selected %>%
  mutate(runtime = na_if(runtime, 0))

movies_runtime %>% 
  summarise(count = sum(is.na(runtime)))
```

```{r}
movies_imputed <- movies_runtime %>%  
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed %>% 
  summarise(count = sum(is.na(runtime)))
```

```{r}
movies_imputed %>% 
  slice_min(runtime, n = 10)
```

```{r}
movies_imputed %>% 
  slice_max(runtime, n = 10)
```

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget < 100, median(budget), budget))
```

Question 3

```{r}
movies_selected %>% 
  summarise(na_runtime = sum(is.na(runtime)),
            na_title = sum(is.na(title)),
            na_budget = sum(is.na(budget)))
```

Question 4

There’s not too many NAs, but there are actually quite a few movies with a runtime of 0 in this dataset. Since it’s impossible for a movie to have a runtime of 0, use the function na_if to convert runtimes of length 0 into NAs. Save this into a new variable called movies_runtime. Then count how many missing values there are now in the column runtime.

```{r}
movies_runtime <- movies_selected %>% 
  mutate(runtime = na_if(runtime, 0))

movies_runtime %>% 
  summaries(count = sum(is.na(runtime)))
```

Question 5

Impute the missing values in runtime with the median runtime using coalesce and save this into a new variable called movies_imputed. There should now be no missing values in the column runtime - check this to make sure.

```{r}
movies_imputed <- movies_runtime %>% 
  mutate(runtime = coalesce(runtime, median(runtime, na.rm = TRUE)))

movies_imputed %>% 
  summarise(count = sum(is.na(runtime)))
```

Question 6 
Finally, use the slice_min and slice_max functions on movies_imputed to get the movies with the 10 shortest and 10 longest runtimes.

```{r}
movies_imputed %>% 
  slice_min(runtime, n = 10)
```

```{r}
movies_imputed %>% 
  slice_max(runtime, n = 10)
```

```{r}
?slice_max
```


Question 7 

Using the if_else function, impute anything with a budget below $100 with the median budget. Overwrite your movies_imputed so it contains the new budget values.

```{r}
movies_imputed <- movies_imputed %>% 
  mutate(budget = if_else(budget < 100, median(budget), (budget))
```



** Extension **

Question 1

Using case_when, create a new column called budget_type and label budgets as follows:

    Budgets below 12 million as ‘Small budget’
    Budgets between 12 and 40 million as ‘Medium budget’
    Budgets 40 millions and above as ‘Big budget’

Save this into a new variable called movie_budgets.

```{r}
movie_budgets <- movies_imputed %>% 
  mutate(
    budget_type = case_when(
      budget < 12e6 ~ "Small budget",
      budget < 40e6 ~ "Medium budget",
      budget >= 40e6 ~ "Big budget"
    )
  )
```

Question 2

Take the original dataset with all the variables. Using across and where, summarise the number of missing values, first across all columns of type character, and then across all columns of type numeric.

```{r}
movies %>% 
  summarise(across(where(is.numeric), ~sum(is.na(.x))))
```

```{r}
movies %>% 
  summarise(across(where(is.character), ~sum(is.na(.x))))
```

```{r}
movies %>% 
  head (10)
```

```{r}
movies %>% 
  tail(10)
```

```{r}
movies %>% 
  arrange(desc(budget))
```

```{r}
movies %>% 
mutate(profit = revenue - budget,
       .after = revenue) %>% 
  arrange(desc(profit))
```

```{r}
movies %>% 
  filter(vote_count > 1000) 
  arrange(desc(vote_average))
```

```{r}
movies %>% 
  select(title, vote_average) %>% 
  mutate(any_good = case_when(
    vote_average < 3.9 ~ "Poor",
    vote_average < 5.4 ~ "Mediocre",
    vote_average < 6.9 ~ "Good",
    vote_average < 8.4 ~ "Great", 
    vote_average > 8.5 ~ "Masterpiece"
  ))
```

```{r}
movies %>% 
   mutate(budget = if_else(budget < 100, median(budget), budget))
```

