---
title: "Homework Week 5 Day 1"
output: html_notebook
---

```{r}
library(tidyverse)
library(CodeClanData)
```

```{r}
qb_revenue_breakdown
```

# Question 1.

#Take the data in the dataset qb_revenue_breakdown and make a stacked bar chart showing the sources of revenue across the two years in the dataset. 

```{r}
ggplot(qb_revenue_breakdown) +
  geom_bar(aes(x = Product, y = Revenue, fill = Year), stat = "identity") +
  labs(title = "Revenue Breakdown") +
  theme_linedraw()
  
```

# Question 2.
#Make a line chart showing monthly sales of the “flagship product” - the ‘KwikBit Unit 1’ - over the last year. This data is inside qb_monthly_sales, but you will need to use filter() or subset() (base R).

```{r}
qu_unit_1_monthly_sales <- qb_monthly_sales %>% 
  filter(Cashflow == "Kwikbit Unit 1 Sales")
```

```{r}
ggplot(qu_unit_1_monthly_sales) +
  geom_line(aes(x = Date, y = Amount)) +
  labs(title = "Kwikbit Sales") +
  theme_linedraw()
```

# Question 3.
#Make a line chart showing monthly revenue and costs over the last year. This data is also in qb_monthly_sales.

```{r}
qb_profit <- qb_monthly_sales %>% 
  filter(Cashflow != "Kwikbit Unit 1 Sales")
```

```{r}
ggplot(qb_profit) +
  geom_line(aes(x = Date, y = Amount, colour = Cashflow)) +
  ylim(0,3000) +
  labs(Title = "QB Profit") +
  theme_linedraw()
```

# Question 4.
#Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot (use geom_area). This data is in qb_competitors. 

```{r}
qb_competitors
```
```{r}
qb_competitors %>% 
mutate(revenue_thousands = Revenue/1000) %>% 
ggplot() +
  geom_area(aes(x = Year, y = revenue_thousands, colour = Company)) +
  ylab("Revenue (1000 units)") +
  theme_linedraw() +
  labs(title = "QB Competitors")
```

# Question 5.
#Now show the sales from the four competitors as a line graph. Include an extra layer that shows the data points used to make the lines. 

```{r}
ggplot(qb_competitors) +
  geom_line(aes(x = Year, y = Revenue, colour = Company)) +
  geom_point(aes(x = Year, y = Revenue, colour = Company)) +
  theme_linedraw() +
  labs(title = "QB Competitors")
```

# Question 6.
#Now the company wants to compare the number of steps that their device counts vs. their competitors. Make a line graph of the number of steps throughout time, and use faceting to compare between companies and people. The data for this is in qb_device_data. 

```{r}
qb_device_data
```

```{r}
ggplot(qb_device_data) +
  geom_line(aes(x = hours, y = counts), stat = "identity") +
  facet_grid(device ~ id) +
  labs(title = "I don't think this one is right")
```

