---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
# Recoding excercise

```{r}
inmates <- read_tsv("../data/inmates.tsv")
```

# 1 Change the ‘M’/‘F’ values in gender to be ‘Male’/‘Female’.

```{r}
inmates %>% 
  mutate(gender = recode(gender, "M" = "Male", "F" = "Female"))
```

# 2.For the race variable, everything is in capital letters, change each level to title case. Also combine ‘AMER IND’ and ‘ASIAN’ into an ‘Other’ category.

```{r}
inmates %>% 
  mutate(race = recode(race, "WHITE" = "White", "BLACK" = "Black", 
                       "HISPANIC" = "Hispanic", .default = "Other"))
```


# 3. Make a new variable bond_level which is High whenever the bond for an inmate is above $1,000,000 and Normal otherwise.

```{r}
inmates_bond <- inmates %>% 
  mutate(bond_level = case_when(
    bond_amount > 1000000 ~ "High",
    TRUE ~ "Normal"),
    .after = bond_amount)
```

# 4. How many inmates have a high bond level?

```{r}
inmates_bond %>% 
  count(bond_level)
```

# 5. Modify the detainer variable so that NONE, IMIGRATION and FEDERAL are in title case and all other levels are set to Other.

```{r}
inmates %>% 
  mutate(detainer = recode(detainer, "NONE" = "None", "IMMIGRATION" = "Immigration", "FEDERAL" = "Federal", .default = "Other"))
```



