---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(CodeClanData)
library(ggplot)
```
```{r}
msleep <- data("msleep")

rm(msleep)


```

# Question 2.

Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

Confidence level = 5% 

HO is that the sleep_total of all animals will be the same as Jabberwockies at 7 hours.

Null hypothesis is mu_sleep_total = 7

Ha is that the sleep_total of all animals will be greater or less than the sleep of Jabberwockies

Alternative hypothesis is mu_sleep_total <> 7

```{r}
msleep_mean <- msleep %>% 
  summarise(av_total_sleep = mean(sleep_total))
```

```{r}
library(infer)
```

```{r}
null_distribution_jab <- msleep %>% 
  specify(response = sleep_total) %>% 
  hypothesise(null = "point", mu = 7) %>% 
  generate(reps = 10000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

```{r}
null_distribution_jab %>% 
  visualise(bins = 30)
```

```{r}
null_distribution_jab %>% 
  visualise(bins = 30) +
  shade_pvalue(obs_stat = msleep_mean,
               direction = "both")
```

```{r}
p_value_jab <- null_distribution_jab %>% 
  get_pvalue(obs_stat = msleep_mean,
             direction = "both")
```

We reject our Null Hypothesis as the amount of time jabberwockies sleep is significantly less than the average time slept for all animals in the data set. 

# Question 3 

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.

HO is that omnivores do not sleep significantly longer than herbivores

(mu_sleep_omnivores - mu_sleep_herbivores) = 0

Ha is that omnivores sleep significantly longer than herbivores

(mu_sleep_omnivores - mu_sleep_herbivores) = < 0

alpha = 5%

```{r}
sleep_difference <- msleep %>% 
  group_by(vore) %>% 
  drop_na(vore) %>% 
  summarise(mean_sleep = mean(sleep_total)) %>% 
  filter(vore == "omni")
```
The average sleep time for herbivores is 9.5 and for omnivores it is 10.9
```{r}
null_dist <- sleep_difference %>% 
  specify(response = mean_sleep) %>% 
  hypothesise(null = "point", mu = 9.5) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

# wrong answer

# copied answer

```{r}
null_distribution <- msleep %>%
  filter(vore %in% c("omni", "herbi")) %>%
  specify(sleep_total ~ vore) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 10000, type = "permute") %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))

obs_stat <- msleep %>%
  filter(vore %in% c("omni", "herbi")) %>%
  specify(sleep_total ~ vore) %>%
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_distribution %>%
  visualise() +
  shade_p_value(direction = "right", obs_stat = obs_stat)
```

```{r}
null_distribution %>%
  get_p_value(direction = "right", obs_stat = obs_stat)
```


# Question 4 

Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%. 

```{r}
msleep_domesticated <- msleep %>% 
  mutate(domesticated = case_when(
    conservation == "domesticated" ~ "Yes",
    .default = "No"))
```


```{r}
obs_stat <- msleep_domesticated %>% 
  summarise(prop = sum(domesticated == "Yes")/n())
```
```{r}
null_distribution <- msleep_domesticated %>% 
  specify(response = domesticated,
          success = "Yes") %>% 
  hypothesise(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "draw") %>% 
  calculate(stat = "prop")
```

```{r}
null_distribution %>% 
  visualise(bins = 30) +
shade_pvalue(obs_stat = obs_stat,
             direction = "less")
```

```{r}
null_distribution %>% 
get_pvalue(obs_stat = obs_stat,
             direction = "greater")
```

We can confidently reject the null hypothesis as there is a high chance that the proportion of domesticated animals is above 5%. 

# 1.2 Hypothesis testing - Defining the Hypothesis

# Question 1

Coffee Shop

What kind of test you would use?

 - One sample test, calculating the proportion of people who recognise the cafe.

H0 and Ha in both mathematical notation and in words.

HO the percentage of recognition of the cafe is equal to or less than 40%
HA the percentage of recognition of the cafe is greater than 40% 

HO: (prop_recognise_cafe) =< 40%
HA: (prop_recognise_cafe) > 40%

Also state the method you would use to generate the null distribution (bootstrap, permutation or draw). Draw. 

# Question 2 

AB Testing

What kind of test you would use?

 - Two sample test of paired samples. Calculating the different CTR of each different type of web page.

H0 and Ha in both mathematical notation and in words.

HO there is no difference in the CTR of each website.
HA there is a greater number of clicks through to the banner at the top of the website (group B). 

HO: (CTR_Group_B - CTR_Group_A) = 0
HA: (CTR_Group_B - CTR_Group_A) > 0

Also state the method you would use to generate the null distribution (bootstrap, permutation or draw). Bootstrap. 

# Question 3 

Part sizes at 145mm 

What kind of test you would use?

 - Single sample tests getting the mean size of the 200 parts
 
H0 and Ha in both mathematical notation and in words.

HO - There is no change in the part sizes and they stay consistently at a mean of 145mm

Ha - The part mean sizes will have either increased or decreased in size from 145mm

HO: (mu_ave_part_size) = 145
HA: (mu_ave_part_size) <> 145

Also state the method you would use to generate the null distribution (bootstrap, permutation or draw). Bootstrap

# 1.3 Hypothesis Testing - Interpreting the results

# Question 1.

Coffee shop problem: With a p-value of 7% we can reject the null hypothesis and find that more than 40% of people in the town have heard of the independent coffee shop. However it is a higher proportion than our significance level.

# Question 2.

Website company problem: With a confidence level of 1% they were confident the experiment should work and were right to do so as the p-value was 0.6% so we can reject the null hypothesis and find that there was a higher CTR for option B over option A. 

# Question 3 

Manufacturing company problem: With a p-value of 55% we have to accept the null hypothesis is more likely to be correct and that the mean of the parts is more likely to be 145mm. 