---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(GGally)
library(pROC)
library(modelr)
library(caret)
```

```{r}
orange <- read_csv("data/orange_juice.csv")
orange_dic <- read_csv("data/data_dict.txt")
```

```{r}
orange_juice <- orange %>% 
  clean_names() %>% 
  mutate_if(is_character, as_factor) %>% 
  select(-c(price_ch, price_mm, store_id, price_diff, list_price_diff))
  
```

```{r}
alias(purchase ~ ., data = orange_juice)
```


```{r message=FALSE, warning=FALSE}
ggpairs(orange_juice)
```

My hypothesis is that the following factors will influence people to buy Citrus Hill more over Minute Maid. Discounts on Citrus Hill and Minute Maid, loyal_ch where people have their loyalty measured in citrus hill. 

```{r}
model_all <- glm(purchase ~ .,
                 data = orange_juice,
                 family = binomial(link = "logit"))

summary(model_all)
```
Looking at the numbers and p-values of the factors it would seem my hypothesis was not quite right. Whilst loyal_ch and discount_mm did have low p-values, discount_ch did not and there were several other factors which had lower p-values which I did not mention like sale_price, store7 and pct_disc_mm. 

I will make three models to compare, the first is just loyal_ch, the second will include all factors I have listed above and the last will be the top 3 factors which give a price comparison to citrus hill over minute maid. 

```{r}
juice_logreg_modela <- glm(purchase ~ loyal_ch,
                           data = orange_juice,
                           family = binomial(link = "logit"))

summary(juice_logreg_modela)
```

```{r}
juice_logreg_modelb <- glm(purchase ~ loyal_ch + disc_mm + sale_price_mm + sale_price_ch + store7 + pct_disc_mm,
                           data = orange_juice,
                           family = binomial(link = "logit"))

summary(juice_logreg_modelb)
```

```{r}
juice_logreg_modelc <- glm(purchase ~ disc_mm + sale_price_mm + sale_price_ch + pct_disc_mm,
                           data = orange_juice,
                           family = binomial(link = "logit"))
summary(juice_logreg_modelc)
```


```{r}
juice_data_a <- orange_juice %>% 
  add_predictions(juice_logreg_modela, type = "response")

head(juice_data_a)
```

```{r}
juice_data_b <- orange_juice %>% 
  add_predictions(juice_logreg_modelb, type = "response")
```

```{r}
juice_data_c <- orange_juice %>% 
  add_predictions(juice_logreg_modelc, type = "response")
```

```{r}
roc_juice_moda <- juice_data_a %>% 
  roc(response = purchase, predictor = pred)

roc_juice_modb <- juice_data_b %>% 
  roc(response = purchase, predictor = pred)

roc_juice_modc <- juice_data_c %>% 
  roc(response = purchase, predictor = pred)
```

```{r}
roc_curve <- ggroc(
  data = list(
    mod1 = roc_juice_moda, 
    mod2 = roc_juice_modb,
    mod3 = roc_juice_modc
  ), 
  legacy.axes = TRUE) +
  coord_fixed()

roc_curve
```

```{r}
auc(roc_juice_moda)
```

```{r}
auc(roc_juice_modb)
```

```{r}
auc(roc_juice_modc)
```

```{r}
train_control <- trainControl(method = "repeatedcv",
                              number = 5,
                              repeats = 100,
                              savePredictions = TRUE,
                              classProbs = TRUE,
                              summaryFunction = twoClassSummary)
```

```{r}
modela <- train(purchase ~ loyal_ch,
                data = orange_juice,
                trControl = train_control,
                method = "glm",
                family = binomial(link = "logit"))

summary(modela)
```

```{r}
modelb <- train(purchase ~ loyal_ch + disc_mm + sale_price_mm + sale_price_ch + store7 + pct_disc_mm,
                data = orange_juice,
                trControl = train_control,
                method = "glm",
                family = binomial(link = "logit"))

summary(modelb)
```

```{r}
modelc <- train(purchase ~ disc_mm + sale_price_mm + sale_price_ch + pct_disc_mm,
                data = orange_juice,
                trControl = train_control,
                method = "glm",
                family = binomial(link = "logit"))

summary(modelc)
```

