---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(gtools)
```

```{r}
titanic <- read_csv("data/titanic.csv")
```

```{r}
titanic_crew <- titanic %>% 
  mutate(status = case_when(
    class == "1st" ~ "passenger",
    class == "2nd" ~ "passenger",
    class == "3rd" ~ "passenger",
    .default = "crew"
  ))
```

# Working out the survival rate of the crew

```{r}
titanic_crew_deaths <- titanic_crew %>% 
  filter(survived == "no" & status == "crew") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()
      
titanic_crew_total <- titanic_crew %>% 
  filter(status == "crew") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()

titanic_crew_deaths / titanic_crew_total
```

The total death rate for the Titanic crew was 76.3%.

```{r}
titanic_crew_survived <- titanic_crew %>% 
  filter(survived == "yes" & status == "crew") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()
      
titanic_crew_total <- titanic_crew %>% 
  filter(status == "crew") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()

titanic_crew_survived / titanic_crew_total
```

The survival rate for the Titanic crew was 23.7%. 


# Working out the survival rate of the passengers

```{r}
titanic_passenger_deaths <- titanic_crew %>% 
  filter(survived == "no" & status == "passenger") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()

titanic_passenger_total <- titanic_crew %>% 
  filter(status == "passenger") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()

titanic_passenger_deaths / titanic_passenger_total
```

The death rate for passengers was 62%. 

```{r}
titanic_passenger_survived <- titanic_crew %>% 
  filter(survived == "yes" & status == "passenger") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()

titanic_passenger_total <- titanic_crew %>% 
  filter(status == "passenger") %>% 
  summarise(p = n()/nrow(titanic_crew)) %>% 
  pull()

titanic_passenger_survived / titanic_passenger_total
```

The survival rate for Titanic passengers was 38%. 

# Conclusion: there is a clear difference that passengers on the Titanic were much more likely to survive than their crew counterparts. 

# 1.2 Probability Consolidation Questions

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
c <- rolldie(1)
c

lower_than_five <- c %>% 
  filter(X1 < 5)
lower_than_five

prob_total_five <- nrow(lower_than_five)/nrow(c)
prob_total_five
```

# The odds of a dice rolling lower than five is 66.7%

2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
s_three_dice <- rolldie(3)
s_three_dice

s_three_dice %>% 
  summarise(size_of_s = n())
```

# If three are rolled there there can be 216 different outcomes.

3. In an experiment where we roll four dice:

how many outcomes are in the event where the total of the four dice equals 5, 6 or 7?

```{r}
four_dice <- rolldie(4)
four_dice

four_dice %>% 
  summarise(size_of_s = n())

four_dice %>% 
  
```

what is the probability of this event?
what assumptions do we apply in answering part ii?


4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?


```{r}
chair_height <-c("person1", "person2", "person3", "person4", 
                "person5")

five_chairs <- combinations(n=5,r=5,v=chair_height, repeats.allowed = TRUE)
five_chairs

1/126
```

# There is a 1/126 chance (0.8%) of them sitting in the correct order from decreasing height, left to right. 

5. I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?

```{r}
six_dice <- rolldie(6)
six_dice

six_dice %>% 
  summarise(size_of_s = n())
```
# The odds of rolling a set of six dice 6-1, left to right is 1/46656. 
    
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?

6. If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades? 

# 50% odds
