---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)

ames <- read_csv("ames.csv")

ames <- clean_names(ames)
```

# Task 2.
Investigate the distribution of lot_area. Is the distribution roughly normal? If not, what problems do you find?

```{r}
ames %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram(colour = "white")
```

The graph peaks very early around the average but there are a few outliers in the data that give it a long tail. 

```{r}
ames %>% 
  summarise(mean_lot_area = mean(lot_area))
```

# Task 3.

Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.

```{r}
bootstrap_house_sample <-ames %>% 
  rep_sample_n(size = 200, replace = TRUE, reps = 5000) %>% 
  summarise(mean_lot_area = mean(lot_area))

bootstrap_house_sample
```

```{r}
bootstrap_house_sample %>% 
  ggplot(aes(x = mean_lot_area)) +
  geom_histogram(colour = "white")
```

The bootstrapped sample has a wide distribution. 

# Task 4

Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution

```{r}
ci_95_house <- bootstrap_house_sample %>% 
  summarise(mean = mean(mean_lot_area),
            lower_bound = quantile(mean_lot_area, probs = 0.025),
            upper_bound = quantile(mean_lot_area, probs = 0.975)
            )
```

```{r}
library(infer)
```

```{r}
infer_ci_95_house <- bootstrap_house_sample %>% 
   get_confidence_interval(level = 0.95, type = "percentile")
infer_ci_95_house
```

```{r}
bootstrap_house_sample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95_house)
```

# Task 5
Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?


```{r}
infer_ci_99_house <- bootstrap_house_sample %>% 
   get_confidence_interval(level = 0.99, type = "percentile")
infer_ci_99_house
```

```{r}
bootstrap_house_sample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99_house)
```


The distribution is much wider than 95% because it is taking in a larger proportion of lots. 

# Task 6

Calculate the point estimate of the mean(lot_area)


```{r}
bootstrap_house_sample %>% 
  summarise(mean(mean_lot_area))
  
```

```{r}
ames_1920 <- ames %>% 
  filter(year_built < 1920)
```

```{r}
sample_1920_200 <- ames_1920 %>% 
  rep_sample_n(size = 200, replace = TRUE, reps = 200) %>% 
  summarise(mean = mean(lot_area))
```

```{r}
infer_sample_1920 <- sample_1920_200 %>% 
  get_confidence_interval(level = 0.95, type = "percentile")
infer_sample_1920
```
```{r}
sample_1920_200 %>% 
  summarise(mean(mean))
```


```{r}
sample_1920_50000 <- ames_1920 %>% 
  rep_sample_n(size = 200, replace = TRUE, reps = 50000) %>% 
  summarise(mean = mean(lot_area))
```

```{r}
infer_sample_50000 <- sample_1920_50000 %>% 
   get_confidence_interval(level = 0.95, type = "percentile")
infer_sample_50000
```
```{r}
sample_1920_50000 %>% 
  summarise(mean(mean))
```

